We are not the 99 percent: the Local Group as an outlier in galaxy pairs' satellite distributions

### 2017-10-28 paper/paper.tex
new table + abstract

%=========================================================================
\usepackage{amsmath} 
\usepackage{amssymb} 
\usepackage{graphicx}
\usepackage{grffile}
\usepackage[dvips]{epsfig}
\usepackage{epsfig}  
\usepackage{color}
\usepackage{caption}
\usepackage{hyperref}
\usepackage{bm}
%Non reposionated tables

@@

\begin{abstract}
In this paper we quantify the joint spatial distribution of the brightest satellites
around the Milky Way (MW) and M31, the dominant galaxies in the Local
Group (LG).
We use the Illustris-1 and ELVIS simulations to quantify how the 
unusual satellite distribution in the MW  makes the LG an atypical pair in
the broader cosmological context provided by LCDM simulations. 
We find that only $0.05\%$ to $0.25\%$ of the pairs with isolation
and dynamical characteristics similar to the LG are expected to have
satellite distributions with the same degree of atipicality, making
the LG a $3\sigma$ outlier.
\end{abstract}

@@

>>>>

%=========================================================================
\usepackage{amsmath} 
\usepackage{amssymb} 
\usepackage{multirow}

\usepackage{graphicx}
\usepackage{grffile}
\usepackage[dvips]{epsfig}
\usepackage{epsfig}  
\usepackage{color}
\usepackage{caption}
\usepackage{hyperref}
\usepackage{bm}
%Non reposionated tables

@@

\begin{abstract}
In this paper we quantify the joint spatial distribution of the brightest satellites
around the Milky Way (MW) and M31, the dominant galaxies in the Local
Group (LG).
We use the Illustris-1 and ELVIS simulations to quantify how the 
unusual satellite distribution in the MW  makes the LG an atypical pair.
A crucial aspect in our analysis is that we define the atypicallity as
the degree at which a satellite distribution deviates from sphericity and
not as a deviation from simulations.
We find that only $0.05\%$ to $0.25\%$ of the pairs with isolation
and dynamical characteristics similar to the LG are expected to have
satellite distributions with the same degree of atipicality, making
the LG a $3\sigma$ outlier.
\end{abstract}

@@

M31 observations

\begin{table*}
  \centering
  \renewcommand{\arraystretch}{1.2}
  \begin{tabular}{|p{2.5cm}|c|c|c|c|c|c|c|c|}
    \hline
    \multirow{2}{4.0cm}{} & \multicolumn{2}{c|}{\textbf{Observations}} & \multicolumn{2}{c|}{\textbf{Randomized Obs.}} & \multicolumn{2}{c|}{\textbf{Illustris-1}} & \multicolumn{2}{c|}{\textbf{ELVIS}}\\
    % \hline
    % \textbf{Inactive Modes} & \textbf{Description}\\
    \cline{2-9}
    & \textbf{M31} & \textbf{MW} & \textbf{M31} & \textbf{MW} & \textbf{M31} & \textbf{MW}& \textbf{M31} & \textbf{MW}\\
    %\hhline{~--}
    \hline
    Plane width (kpc) & $59\pm 3$  & $22\pm 2$  & $65\pm 11$   & $45\pm 8$     & $70\pm 4$ & $67\pm 2$ & $70\pm 2$& $68\pm 4$ \\\hline
    $c/a$ ratio & $0.67\pm 0.03$ & $0.53\pm 0.03$ & $0.75\pm0.07$ & $0.72\pm 0.07$ & $0.72\pm 0.01$ & $0.72\pm 0.01$ & $0.73\pm 0.01$& $0.69\pm 0.01$ \\ \hline
    $b/a$ ratio & $0.90\pm 0.03$ & $0.88\pm 0.01$ & $0.90\pm0.04$ & $0.90\pm 0.04$ & $0.89\pm 0.01$ & $0.89\pm 0.01$ & $0.89\pm0.01$& $0.90\pm 0.01$\\ \hline
  \end{tabular}
  \caption{Mode Transition Times}
\end{table*}
